Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-11-15 packages/spec-haskell/yellowpaper/Paper1.tex

It is based on the insight of the deep connection (equivalence/isomorphism) between logic and
dependently typed programming, often called "the Curry–Howard correspondence", as discovered and
developed during the 20th century (explained in \cite{wadler2015propositions} by Phillip Wadler as
``Propositions as Types''). Agda being a dependently typed functional programming language fully
embodies this insight, hence a good candidate for creating provable correct programs.

>>>>

It is based on the insight of the deep connection (equivalence/isomorphism) between logic and
dependently typed programming, often called ``the Curry–Howard correspondence'', as discovered and
developed during the 20th century (explained in \cite{wadler2015propositions} by Phillip Wadler as
``Propositions as Types''). Agda being a dependently typed functional programming language fully
embodies this insight, hence a good candidate for creating provable correct programs.
